TGI Spinal Analysis Code

### 2023-01-04 analysis/tgi-spinal_analysis.Rmd
pushing to git
marginal effects plotting

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Loading libraries
# check for pacman package and install if not found
if (!require("pacman")) install.packages("pacman")
  pacman::p_load(boot, broom, broom.mixed, brms, car, caret, corrplot, DHARMa, gamlss,
                 ggeffects, gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
                 modelsummary, mumin, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
                 rsample, rstatix, simr, tibble, tidyverse, wesanderson
                 )
```

@@

# Data organisation
```{r}
# transform the ID of participants to remove 0
df_res$ID <- as.numeric(df_res$ID)
# recode conditions
df_res <- df_res %>%
  mutate(condition = recode(condition, '1' = 'within', '2' = 'across'),
         cold_probe = recode(cold_probe, 'C6' = 'rostral', 'T1' = 'caudal',
                             'dist' = 'distal', 'prox' = 'proximal'))
# change levels 
df_res$cold_probe <- factor(df_res$cold_probe, 
                            levels = c("caudal", "rostral", "distal", "proximal"))

@@

Anova(model.cold)
# get Rsq with the mumin package

# Getting the marginal effects for plotting
# First the zeros - create new lm mo
df_long$bin <- ifelse(df_long$VAS == 0, 1, 0)

cold.eff <- glm(bin~1+manipulation, 
                  family = binomial(link = 'logit'),
                  data = df_long %>% filter(quality == 'cold'))
summary(cold.eff)

eff <- ggeffects::ggeffect(cold.eff, terms = c('manipulation'))
plot(eff)

eff <- ggeffects::ggeffect(model.cold, terms = c('condition', 'manipulation', 'cold_cond'),
                           type = 'random', ci.lvl = .95)
plot(eff)
```
# Warm
```{r warmmod}
# Try and model all with ratings
model.warm = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond +
                                trial_n + (1|ID) + (1|order),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_long %>% filter(quality == 'warm'),
                      na.action = na.omit) 
mw <- summary(model.warm)
mw

Anova(model.warm)
```

@@

>>>>

```{r setup, include=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Loading libraries
# check for pacman package and install if not found
if (!require("pacman")) install.packages("pacman")
  pacman::p_load(boot, broom, broom.mixed, brms, car, caret, corrplot, DHARMa, gamlss,
                 ggeffects, gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
                 modelsummary, MuMIn, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
                 rsample, rstatix, simr, tibble, tidyverse, wesanderson
                 )
```

@@

# Data organisation
```{r}
# transform the ID of participants to remove 0
df_res$ID <- as.numeric(df_res$ID)
# recode conditions
df_res <- df_res %>%
  mutate(condition = dplyr::recode(condition, '1' = 'within', '2' = 'across'),
         cold_probe = dplyr::recode(cold_probe, 'C6' = 'rostral', 'T1' = 'caudal',
                             'dist' = 'distal', 'prox' = 'proximal'))
# change levels 
df_res$cold_probe <- factor(df_res$cold_probe, 
                            levels = c("caudal", "rostral", "distal", "proximal"))

@@

Anova(model.cold)
# get Rsq with the mumin package
```
# Marginal effect plots of full model - cold
```{r}
cold_eff <- ggeffects::ggpredict(model.cold, terms = c('cold_cond', 'manipulation', 'condition'),
                           ci.lvl = .95)
# changing labels for plotting
cold_eff$group <- factor(cold_eff$group, labels = c('Non-TGI', 'TGI'))
cold_eff <- cold_eff %>% 
  mutate(label = 
           case_when(facet == 'across' & x == 'prox_caud' ~ 'caudal',
                     facet == 'across' & x == 'dist_rostr' ~ 'rostral',
                     facet == 'within' & x == 'prox_caud' ~ 'proximal',
                     facet == 'within' & x == 'dist_rostr' ~ 'distal',) 
         )

cold_eff$label = factor(cold_eff$label, levels = c('proximal','distal','caudal','rostral'))

# plotting - within
ggplot(data = cold_eff %>% 
         filter(facet == 'within'), 
       aes(label, predicted, group = group, colour = group),) +
  geom_point(position = position_dodge(.3)) +
  geom_line(position = position_dodge(.3)) +
  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
                position = position_dodge(.3), width = .1) +
  ylim(0.1, 0.5) +
  theme_bw()
# plotting - across
ggplot(data = cold_eff %>% 
         filter(facet == 'across'), 
       aes(label, predicted, group = group, colour = group),) +
  geom_point(position = position_dodge(.3)) +
  geom_line(position = position_dodge(.3)) +
  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
                position = position_dodge(.3), width = .1) +
  ylim(0.1, 0.5) +
  theme_bw() +
  theme(legend.title = element_blank())
```

# Warm
```{r warmmod}
# Try and model all with ratings
model.warm = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond +
                                trial_n + (1|ID) + (1|order),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_long %>% filter(quality == 'warm'),
                      na.action = na.omit) 
mw <- summary(model.warm)
mw

Anova(model.warm)

eff <- ggeffects::ggeffect(model.warm, terms = c('cold_cond','condition'),
                           type = 'random', ci.lvl = .95)
plot(eff)
```

@@

# Zero inflation marginal effects plot of all models
```{r zero_plots}
# Getting the marginal effects for plotting
# First the zeros - create new lm mo
df_long$bin <- ifelse(df_long$VAS == 0, 1, 0)

# model for each VAS
cold.eff <- glm(bin~1+manipulation, 
                  family = binomial(link = 'logit'),
                  data = df_long %>% filter(quality == 'cold'))
summary(cold.eff)

# Data-frames
cold_zeff <- ggeffects::ggeffect(cold.eff, terms = c('manipulation'))
# changing labels for plotting
cold_zeff$x <- factor(cold_zeff$x, labels = c('Non-TGI', 'TGI'))

# plotting
ggplot(cold_zeff, aes(x, predicted)) +
  geom_point() +
  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
                width = .1) +
  theme_bw()
